---
title: "Rhizo-Meso Distance"
output:
  html_document:
    df_print: paged
---
This plot shows that Rhizomelia is a child of Disproportionate Short Stature and also of Limb Undergrowth:
```{r}
BiocManager::install("Rgraphviz")
library(ontologyIndex)
library(ontologyPlot)
library(ontologySimilarity)
data(hpo)

Rhizomelia <- "HP:0008905"
Mesomelia <- "HP:0003027"
Disproportionate_short_stature <- "HP:0003498"

onto_plot(hpo, terms=get_ancestors(hpo, c(Disproportionate_short_stature, Rhizomelia)))
```
While this plot shows that Mesomelia is a child of Limb Undergrowth but not of Disproportionate Short Stature:
```{r}
onto_plot(hpo, terms=get_ancestors(hpo, c(Disproportionate_short_stature, Mesomelia)))
```
As a result, the semantic similarity between Rhizomelia and Disproportionate Short Stature is high:
```{r}
get_term_sim_mat(ontology = hpo,
                 information_content = descendants_IC(hpo),
                 row_terms = Disproportionate_short_stature,
                 col_terms = Rhizomelia)
```
but the semantic similarity between Mesomelia and Disproportionate Short Stature is low:
```{r}
get_term_sim_mat(ontology = hpo,
                 information_content = descendants_IC(hpo),
                 row_terms = Disproportionate_short_stature,
                 col_terms = Mesomelia)
```

On the other hand, as rhizo and mesomelia are linked through Limb Undergrowth, the similarity between rhizo and mesomelia is still high, so dont use that as an example.
```{r}
onto_plot(hpo, terms=get_ancestors(hpo, c(Rhizomelia, Mesomelia)))
```

